Inferring Invariants of Distributed Programs

### 2015-03-04 Doc/evalrelate.tex
Edited Related Work

\section{Evaluation Methodology}
We will implement our approach in a tool in Go programming language. We plan to evaluate our tool by verifying correctness of two phase commit and leader election protocols. Our tool should be able to infer safety property of both algorithms. In two phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property. In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property). It is worth mentioning that our approach is not suitable for checking the liveness properties of these algorithms.

@@

Beschastnikh et al. \cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system. By using logs of the system, they put the responsibility on developers to decide which portion of state of the program can be used to infer invariants. We require developers to specify at which points in program invariants can be checked but we infer the portion of the state that can be checked for invariants automatically with data flow analysis.

\section{Acknowledgment}
We thank Ivan Beschastnikh for his valuable feedback on initial drafts of this proposal.

>>>>

\section{Evaluation Methodology}
We will implement our approach in a tool in Go programming language. We plan to evaluate our tool by verifying correctness of two-phase commit and leader election protocols. Our tool should be able to infer safety property of both algorithms. In two-phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property. In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property). It is worth mentioning that our approach is not suitable for checking the liveness properties of these algorithms.

@@

Beschastnikh et al. \cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system. By using logs of the system, they put the responsibility on developers to decide which portion of the state of the program can be used to infer invariants. Although, we require developers to specify at which points in the program invariants can be checked, we infer the portion of the state that can be checked for invariants automatically with data flow analysis.

\section{Acknowledgment}
We would like to thank Ivan Beschastnikh for his valuable insight and feedback on initial draft of this proposal.
